---
title: "maps"
author: "steppe"
date: "3/22/2022"
output: pdf_document
---

```{r Load Libraries, warning = F, message = F}
shhh <- suppressPackageStartupMessages
#set_here(path = "/hdd/revisionary_taxonomy")
shhh(library(here))
shhh(library(tidyverse))
shhh(library(sf))
shhh(library(tigris))
shhh(library(ggspatial))
source('functions.R')
rm(shhh)
```

```{r import plant data, echo = F}
astragalus <- st_read(paste0(here(), '/data/processed/', 'astragalus.shp'), quiet = T)
eriogonum <- st_read(paste0(here(), '/data/processed/', 'eriogonum.shp'), quiet = T)
townsendia <- st_read(paste0(here(), '/data/processed/', 'townsendia.shp'), quiet = T)
```

```{r Create Boundary boxes, echo = F}
pts <- bind_rows(astragalus, eriogonum, townsendia) %>% 
  st_transform(4269) 

bb <- pts %>% 
  st_transform(32613) %>% 
  st_buffer(50000) %>% 
  st_transform(4269) %>% 
  st_convex_hull() %>% 
  st_bbox()
bb1 <- pts %>% 
  st_transform(32613) %>% 
  st_buffer(7500) %>% 
  st_transform(4269) %>% 
  st_convex_hull() %>% 
  st_bbox()

rm(astragalus, eriogonum, townsendia)
```


```{r download political boundaries, eval = F}
counties_filt <- tigris::counties(state = c('AZ', 'CO', 'UT', 'NM'))
counties_filt <- st_crop(counties_filt, bb)

st_write(counties_filt, paste0(here(), '/data/processed/counties.shp'))
```

```{r Evaluate downloaded Political Data}
counties_filt <- st_read(paste0(here(), '/data/processed/counties.shp'), 
                         quiet = T)
counties_filt1 <- st_cast(counties_filt, 'MULTILINESTRING')
  
rm(bb)
```

We will download  basemap for making a large overview map
```{r download a basemap, eval = F}
bb2 <- bb1
names(bb2) <- c('left', 'bottom', 'right', 'top')
basemap <- ggmap::get_stamenmap(bb2,  maptype = "terrain")

coarse_basemap <- tempfile(tmpdir = paste0(here(), '/data/processed/'))
saveRDS(basemap, file = coarse_basemap)
rm(bb2, coarse_basemap)
```

```{r Import basemap from Local}
basemap <- readRDS(paste0(here(), "/data/processed//file82021d31710"))

ggmap::ggmap(basemap) +
  geom_sf(data = counties_filt1, inherit.aes = FALSE,) +
  geom_sf(data = pts, aes(color = scntfcN), inherit.aes = FALSE,) +
  coord_sf(xlim = c(bb1[1], bb1[3]), ylim = c(bb1[2], bb1[4])) +  
  theme_bw() 
```

## Download and process Road Data
```{r Download roads data for relevant counties and subset, eval = F}

counties <- st_intersects(counties_filt, pts)
counties <- counties %>% # find counties which intersect
  map(~ if_else(length(.) > 0, T, F))  %>% 
  unlist()
counties <- counties_filt[counties == TRUE, ]

counties <- bind_rows(counties,
                  counties_filt[counties_filt$NAME %in% c('Montrose','Ouray'),])

lst_result <- apply(counties, 1, john_tigger)
cnty_rds <- bind_rows(lst_result) %>% st_as_sf()
cnty_rds <- st_crop(cnty_rds, bb1) # reduce extent.

st_write(cnty_rds, paste0(here(), '/data/processed/roads.shp'), quiet =T)
rm(counties, lst_result, john_tigger)
```

```{r read in county road data}
cnty_rds <- st_read(paste0(here(), '/data/processed/roads.shp'), quiet =T)
table(cnty_rds$RTTYP)
```

The [US Census Bureau Route Type Codes](https://www.census.gov/library/reference/code-lists/route-type-codes.html), are displayed below for a lookup table.

   Route Type Code  	      Route Type Code Description
--------------------     ---------------------------------
        C 	                      County
        I 	                      Interstate
        M 	                      Common Name
        O 	                      Other
        S 	                      State recognized
        U  	                      U.S.
------------------      ---------------------------------

We will subset this data frame to have a course map for our over map reference maps

```{r Subset to Coarse Roads}
spp_cols <- c(
  'darkorange4', 'darkseagreen4', 
  'slateblue4', 'deeppink4', 
  'tan2', 'thistle4')

rds_coarse <- filter(cnty_rds, RTTYP %in% c('I','U','S')) %>% 
  group_by(FULLNAME) %>% 
  summarize(geometry = st_union(geometry))

topo_base <- ggmap::ggmap(basemap) +
  geom_sf(data = counties_filt1, lty = 3, inherit.aes = FALSE) +
  geom_sf(data = pts, aes(color = scntfcN), inherit.aes = FALSE) +
  geom_sf(data = rds_coarse, inherit.aes = F, colour = 'grey20') +
  scale_color_manual(values= spp_cols)+
  coord_sf(xlim = c(bb1[1], bb1[3]), ylim = c(bb1[2], bb1[4])) +  
  labs(title="Sampled Populations",  x ="", y = "", color = 'Species') +
  theme_bw() +
  theme(axis.text.x=element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.direction = "horizontal"
        ) +
    theme(panel.border = element_rect(colour = "black", fill=NA),
        legend.background = element_rect(linetype = 2, size = 0.5, colour = 1))
  
```


```{r subset finer roads to relevant areas, eval = F}
cnty_rds_local <- cnty_rds %>% filter(! RTTYP %in% c('I','U','S'))
site_adj_roads <- pts %>% 
  st_transform(32613) %>% 
  st_buffer(15000) %>% 
  st_union() %>% 
  st_as_sf() %>% 
  st_transform(4269) %>% 
  st_intersection(., cnty_rds_local)

site_adj_roads <- rmapshaper::ms_simplify(site_adj_roads, keep = 0.5)
site_adj_roads <- st_as_sf(site_adj_roads)

ggmap::ggmap(basemap) +
  geom_sf(data = counties_filt1, lty = 3, inherit.aes = FALSE) +
  geom_sf(data = rds_coarse, inherit.aes = F, colour = 'grey20') +
  geom_sf(data = site_adj_roads, inherit.aes = F) +
  geom_sf(data = pts, aes(color = scntfcN), inherit.aes = FALSE) +
  coord_sf(xlim = c(bb1[1], bb1[3]), ylim = c(bb1[2], bb1[4])) +  
  theme_bw() 

st_write(site_adj_roads, paste0(here(), '/data/processed/roads_nr_sites.shp'), quiet =T)
rm(cnty_rds_local, cnty_rds)
```

```{r read roads back in, eval = F}
site_adj_roads <- st_read(paste0(here(), '/data/processed/roads_nr_sites.shp'), quiet =T)
```


## Determine which plots are in proximity to each other

Each population will have a one page print out, with three plots: 
  - the overview plot of all populations, 
  - a plot within a 16 km boundary box, 
  -  a map of 2.5 km around the population. 
We will work on creating as few of the second plot as possible. We will use a window of 12km, rather than 16km to ensure some points are not squished to the side of maps.


```{r}
rm(cnty_rds, counties_filt, counties_filt1, topo_base, basemap, spp_cols,
   closest_sites, grps_most_dispersed, john_tigger, population_finder, reed_csv, bb1, rds_coarse, target_taxon_grp_fndr)

# raw data
out <- pts %>% 
  split(., 1:nrow(.))%>%
           purrr::map(pts_cell, 
                      utmzone = 32613, 
                      buf_dist = 14000, 
                      out_crs = 4269
                      ) %>% 
  bind_rows() %>% 
  st_as_sf() %>% 
  mutate(rownum = 1:nrow(.), .before = x) %>% 
  st_intersects(., pts)

AB <- window_search(out)  # ident_grp = 64, groups = 66 
k <- gsub('row', '',names(AB))
keepers <- pts[k,]

# first iteration
polys1 <- keepers %>% 
  split(., 1:nrow(.))%>%
           purrr::map(pts_cell,
                      utmzone = 32613, 
                      buf_dist = 16000, 
                      out_crs = 4269) %>% 
  bind_rows() %>% 
  st_as_sf() %>% 
  mutate(POLY_ID = 1:nrow(.))

testput <- window_center(x = pts, y = polys1) %>% 
  st_as_sf()

# Now collect points which just narrowly missed being included in windows
outr <- st_within(pts, testput) 
outr <- unlist(
  lapply(
    as.numeric(outr) == 0, as.numeric
    )
  )

pts1 <- pts[is.na(outr),]
out1 <- pts1 %>% 
  split(., 1:nrow(.)) %>%
           purrr::map(pts_cell, 
                      utmzone = 32613, 
                      buf_dist = 16000, 
                      out_crs = 4269
                      ) %>% 
  bind_rows() %>% 
  st_as_sf()

colnames(out1) <- 'geometry'
st_geometry(out1)  <- 'geometry'
  
windows <- rbind(testput, out1) %>% mutate(windowID = 1:nrow(.))
  
ggplot() +
  geom_sf(data = windows) +
  geom_sf(data = pts) +
  theme_bw()

rm(AB, keepers, out, out1, polys1, pts1, testput, outr, k, pts_cell, window_center, window_search)
```

```{r When overlap exists determine which window a point should be placed in}
testy_d <- st_distance(pts, windows %>% 
  st_centroid())

pts <- cbind(pts, 
                'window' = apply(testy_d, 1, which.min)
             )

ggplot(pts) +
  geom_sf(data = windows) +
  geom_sf(aes(colour = window)) +
  theme_bw()

rm(testy_d)
```

## Download and Save Imagery for each 'Window'

```{r}

wndws_basemap_dl <- function(x){
  
  gg_bb <- st_bbox(x)
  names(gg_bb) <- c('left', 'bottom', 'right', 'top')
  gg_bm <- ggmap::get_stamenmap(gg_bb, zoom = 13, maptype = "terrain")
  
  window_basemap <- paste0(tmpdir = paste0(
    here(), '/data/basemap_imagery/window_bm', x$windowID))
  saveRDS(gg_bm, file = window_basemap)
  
  Sys.sleep(3) # three seconds 
}

windowsL <- split(windows, ~windowID)
lapply(windowsL[3:39], wndws_basemap_dl)

windows_basemap <- paste0(paste0(here(), '/data/basemap_imagery/'),
                          list.files(paste0(here(), '/data/basemap_imagery')
                                     ))
B <- readRDS(windows_basemap[22])


# let us see if we can set this up so that we take the centroid of the rds coarse per window????
ggmap::ggmap(B) +
  geom_sf(data = cnty_rds,  inherit.aes = FALSE, colour = 'grey40') +
  geom_sf(data = rds_coarse, inherit.aes = F, colour = 'grey20') +
  geom_sf_label(data = rds_coarse, aes(label = FULLNAME), inherit.aes = FALSE) +
  geom_sf(data = pts, aes(color = scntfcN), inherit.aes = FALSE, size = 5) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.7, hjust=0.5),
        axis.text.y = element_text(angle = 45, vjust = 0.7, hjust=0.5),
        legend.position = "none") +
  xlab(NULL) +
  ylab(NULL)

```

## download and save imagery for each 'group'

```{r}

```


## Style up and Save the overview basemap

```{r, warning = F}


bb3 <- bb2
names(bb3) <- c('left', 'bottom', 'right', 'top')
basemap_t <- ggmap::get_stamenmap(bb3, zoom = 13, maptype = "terrain")

mapbb <- townsendia %>% filter(rcrdNmb == 761) %>% 
  st_buffer(10000) %>% 
  st_transform(4326) %>% 
  st_bbox() %>% 
  st_as_sfc() %>% 
  st_as_sf()


ggmap::ggmap(basemap) +
  geom_sf(data = counties_filt1, lty = 3, inherit.aes = FALSE) +
  geom_sf(data = rds_coarse, inherit.aes = F, colour = 'grey20') +
  geom_sf(data = pts, aes(color = scntfcN), inherit.aes = FALSE) +
  geom_sf(data = mapbb, fill = NA, color = "red", size = 1.0, inherit.aes = F) +
  scale_color_manual(values= spp_cols)+
  coord_sf(xlim = c(bb1[1], bb1[3]), ylim = c(bb1[2], bb1[4])) +  
  labs(title="Sampled Populations",  x ="", y = "", color = 'Species') +
  theme_bw() +
  theme(axis.text.x=element_blank(),
        axis.text.y = element_blank(),
        plot.title = element_text(hjust = 0.5),
        legend.position="bottom",
        legend.direction = "horizontal",
        panel.border = element_rect(colour = "black", fill=NA),
        legend.background = element_rect(linetype = 2, size = 0.5, colour = 1)) +
  annotation_scale(location = "bl", width_hint = 0.4) +
    annotation_north_arrow(location = "tl", which_north = "true", 
        height = unit(0.8, "cm"),  width = unit(0.6, "cm"),
        pad_x = unit(0.0, "in"), pad_y = unit(0.0, "in"),
        style = north_arrow_orienteering)

```

## Create the itermediate size basemaps